25 years of Social Work Research

### 2015-02-22 dataCleaning.Rmd
Code to merge Ebsco and PQ, remove duplicate records

load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")
```

@@

# Set the working directory
#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
```

>>>>

#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
#load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoPsycInfo.R")

load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoFULL.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/proQuest.R")
load("/Users/SSW/Documents/GitHub/SocialWork100Years/Data/ebscoPsycInfo.R")

```

@@

#Combines EbscoHost and ProQUest wrangles and eliminates duplicate article titles

library(dplyr)

  #Creates variable with highest article ID from ebscohost database
  EbscoIDmax<-max(ebscoBWR.df$articleID)

  #Recodes article ID in ProQuest database in advance of merger with ebscohost
  proQuestBWR.df<-mutate(proQuestBWR.df, articleID=articleID+EbscoIDmax)

  #Creates data frames that contain only article ID and titles from respective
  #databases
  EbscoTitles<-filter(ebscoBWR.df, attributes=="article")
  ProTitles<-filter(proQuestBWR.df, attributes=="article")

  #Combines titles into single data frame
  JointTitles<-rbind(EbscoTitles, ProTitles)

  #Forces article title text to lower case
  JointTitles$record<-tolower(JointTitles$record)

  #Strips out white space and punctuation to ensure small differences
  #in data entry are detected during duplicate elimination
  JointTitles$record<-gsub(" ","", JointTitles$record)
  punct <- '[]\\?!\"\'#$%&(){}+*/:;,._`|~\\[<=>@\\^-]'
  JointTitles$record<-gsub(punct, "", JointTitles$record)

  JointTitles <- JointTitles[duplicated(JointTitles$record), ]

  #Screen out duplicated records by articleID. The articleID must be used
  #because the duplicate title contains other article attributes
  JointTitles.dup.ID <- JointTitles$articleID

  #Combines EbscoHost and ProQuest Wrangles, and strips out article attributes 
  #from duplicate entries
  Combined.DF<-rbind(ebscoBWR.df, proQuestBWR.df)
  Combined.DF<-Combined.DF[!(Combined.DF$articleID %in% JointTitles.dup.ID), ]

```

# Set the working directory
#setwd("/Users/beperron/Git/SocialWorkResearch/Data")
#setwd("/Users/SSW/Documents/GitHub/SocialWork100Years/Data")
```
